---
vignette: |
  %\VignetteIndexEntry{Working Tidyverse: readr, dplyr, stringr} %\VignetteEngine{knitr::rmarkdown} \usepackage[utf8]{inputenc}
author: "Alexis Mekueko"
date: "10/27/2020"
output:
  html_document:
    df_print: paged
  rmarkdown::html_vignette: default
  css: style.css
  pdf_document: default
  vignette: default
title: 'Collaborating and Providing peer to peer Feedback on TidyVerse Assignment'
---



```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 6, tibble.print_max = 6)
```


```{r }

#library(tidyverse) #loading all library needed for this assignment
library(knitr)
#library(readr)
#library(dplyr)
library(stringr)
library(magrittr) # need to check this package

```


# Description
In this assignment, we will extend an existing classmate's work on Tidyverse assignment. In addition we will evaluate the overall classmate's work and annotated code. based on the Instructor guidance. 
The classmates work can be found in the public repo (https://github.com/acatlin/FALL2020TIDYVERSE). We randomly selected submission from Orli Khaimova, BDavidoff and John Mazon. We chose to extend Orli Khaimova's work because her dataset is rich and offered opportunity to practice more tyverse package as we demonstrate below.


Orli Khaimova (23/25):  https://github.com/acatlin/FALL2020TIDYVERSE/blob/master/Orli%20Khaimova%20Create%20tidyverse.Rmd
BDavidoff (23/25) : https://github.com/acatlin/FALL2020TIDYVERSE/blob/master/Tidyverse_Create.Rmd
John Mazon (25/25): https://github.com/acatlin/FALL2020TIDYVERSE/blob/master/tidyverse_johnmazon.Rmd

# Data source
The dataset called 'Avocado Prices' was collected from kaggle.com which was updated by Justin Kiggins 02 years ago. Avocados Prices is about historical data on avocado prices and sales volume in multiple US markets. The dataset is about 2MB.  
https://www.kaggle.com/neuromusic/avocado-prices



# I am a bit lost here...maybe telling your reader what you are about to do (Description). one or two lines...
# R uses factors to handle categorical variables, variables that have a fixed and known set of possible values. Factors are also helpful for reordering character vectors to improve display. The goal of the forcats package is to provide a suite of tools that solve common problems with factors, including changing the order of levels or the values. Some examples include:
https://rdrr.io/cran/forcats/f/README.md


`fct_rev` relevels the levels of a factor in reverse order. In this case, I factored the regions and then used the function in order to put them in reverse alphabetical order. By doing so, I was able to print the regions alphabetically in the graph.

`geom_pointrange` graphs the interval for the average price of avocados for each region. I had to define a ymin and ymax as well. It is useful for drawing confidence intervals and in this case the range of prices.

```{r fig.height = 10, fig.width = 5}

# I think it is good to add some comment so that others understand better your approach or code.

avocados <- read.csv("https://raw.githubusercontent.com/okhaimova/DATA-607/master/avocado.csv")

# let's take a look at avocados details 
str(avocados) # 18249 obs. of  14 variables

#let's check missing data
sum(is.na(avocados))

# I think maybe saving the dataset in a local drive or other storage might be a safe partice
write.csv(avocados,'avocados')
```


# Using dplr package (grammar)
```{r}


```

```{r}
# Example here, I think you want to redefine the data type to date
avocados$Date <- as.Date(avocados$Date)
# redefine year (data type) to character...I thought ideally year is numerical or integer as data type.
# So , I can see you want to do something special with year but I cannot tell
avocados$year <- as.character(avocados$year)
#Good comment
#factors the regions and then using forcats, we reverse the order to make it z-a
avocados$region <- avocados$region %>%
  as.factor() %>%
  fct_rev()
#never done this long grouping for plot...looks good...actually reviewing your code kind of telling me about my own mistake...There is no way to see the result if I don't run ...I think there was option to include a sample result or html version...
# avocados$Date vector contains about 1000 values...a little heavy...I had that problem too.
avocados %>% 
  ggplot(aes(y = AveragePrice, x = region, 
             ymin = AveragePrice-sd(AveragePrice), ymax = AveragePrice+sd(AveragePrice))) +
  geom_pointrange(aes(color = as.factor(region)), size =.01) +
  ylab("Average Price") +
  xlab("Region") +
  ggtitle("Average Price Range") +
  coord_flip() +
  theme(legend.position = "none")



```














